Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems

### 2014-09-13 Report/ieee_journal.tex
Included figure with Q-WSRME

\documentclass[11pt,peerreview,onecolumn,letterpaper]{./../Styles/IEEEtran}

@@

\title{Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
		University of Oulu, Oulu, FI-90014\\
		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
}

@@

>>>>

\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}

@@

\title{Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
	\IEEEauthorblockA{Centre for Wireless Communications (CWC), \\ Department of Communications Engineering (DCE), \\
		University of Oulu, Oulu, FI-90014\\
		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
}

@@

\begin{keywords}
\acs{MIMO}-\acs{OFDM}, weighted sum rate maximization, precoder design, queue driven scheduling and precoder design
\end{keywords}

### 2014-09-13 Report/simulation_results.tex
Included figure with Q-WSRME

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-2}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-2}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

>>>>

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lower path loss. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-3}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-2}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

### 2014-09-13 Report/wsrm_formulation.tex
Included figure with Q-WSRME

In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers obtained
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
\end{subeqnarray}
where \me{\bar{f}(x,x^{(i)})} is the approximate function of \me{f(x)} around the point \me{x^{(i)}}. Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}. It shows that each relaxed formulation converges to the optimal point.

The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders. The monotonic convergence of the objective function can be justified by the following arguments. At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function. Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{x^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well. Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.

>>>>

In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers obtained
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
\end{subeqnarray}
where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}. Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}. It shows that each relaxed formulation converges to the optimal point.

The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders. The monotonic convergence of the objective function can be justified by the following arguments. At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function. Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{\mbf{x}^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well. Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.
